---
title: "Face Name Task Behavioural Study"
output:
  pdf_document: default
  html_document:
    
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---

### Libraries and Functions
```{r message=FALSE, warning=FALSE}
# Clear envirnonment
rm(list = ls())

# Get Libraries and Functions
source("~/Dropbox (Personal)/TI_paper/ti-paper/Data/Functions.R")

```

### Import data and add labels
```{r message=FALSE, warning=FALSE}
# Import data
setwd("~/Dropbox (Personal)/TI_paper/ti-paper/Data/BehaviourStudy/Behaviour")
data_raw <- read_csv("FNAT.csv")


# Assign appropriate Stim factors
data_raw$StimType <- factor(data_raw$StimType)
levels(data_raw$StimType) <- c("Sham", "TI 1:3")

# Assign factors
data_raw$StimType <- factor(data_raw$StimType)
data_raw$block <- factor(data_raw$block)
data_raw$S_ID <- factor(data_raw$S_ID)
data_raw$session <- factor(data_raw$session)
data_raw$Run <- factor(data_raw$Run)
```


### Check data for outliers - Accuracy level
```{r fig.width=12}
g_data <- ddply(data_raw, c("S_ID","session","Run"), summarise,
         N = sum(!is.na(trial)),
         mean_Acc_prct = (sum(Accuracy, na.rm=TRUE)/N)*100
)


pander(g_data)
# All subjects have mean accuracy above 20% (chance level)


ggplot(g_data, aes(x=S_ID, y=mean_Acc_prct, group=session)) + 
    geom_bar(position=position_dodge(), stat="identity") +  geom_hline(yintercept=20, linetype="dashed", color = "red") + facet_grid(.~Run)

# Report values for immediate recall in methods - used as exclusion criteria
subset(g_data, Run == "1") %>% summarise(mean = mean(mean_Acc_prct),
            sd = sd(mean_Acc_prct), min = min(mean_Acc_prct), max = max(mean_Acc_prct))


# For delayed recall
subset(g_data, Run == "2") %>% summarise(mean = mean(mean_Acc_prct),
            sd = sd(mean_Acc_prct), min = min(mean_Acc_prct), max = max(mean_Acc_prct))
```

### Check response distributions
```{r}
## What is the distribution of responses (correct, foil, distractors, omission)
bdata <-  data_raw
bdata$RespType <- ifelse(bdata$Accuracy==1, "Correct", 
       ifelse(bdata$Foil==1, "Foil", 
              ifelse(bdata$Distractor==1, "Distractor", NA)))

# ------- Checking number of cases (percent) -------------

pander(bdata %>% 
    dplyr::group_by(RespType,Run) %>% 
    dplyr::summarise(mean = 100 * n() / (nrow(bdata)/2))) # 2 sessions

# Participants select Correct > Foil > Distractor. They are engaging with the task appropriately. NA = omission

bdata <- bdata[!is.na(bdata$RespType),]  # Getting rid of the few omissions in the dataset
bdata$RespType <- factor(bdata$RespType,levels = c("Correct", "Foil", "Distractor"))

```

### Check the distribution of RTs and clean the data 
```{r}
# ---- Plot histogram of RT  --------
ggplot(bdata, aes(x=RT)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 


# ----- Check 1 and 99% percentiles and remove those from the data ----------
rts <-  bdata$RT
qts <- quantile(rts, probs = c(.01, .99)) 
qts
# 
# 
bdata <- bdata %>% mutate(RT = replace(RT, RT<qts[1], NA))
bdata <- bdata %>% mutate(RT = replace(RT, RT>qts[2], NA))
bdata <- bdata[!is.na(bdata$RT),] 


bdata <- bdata %>% mutate(RT = replace(RT, RT<0.3, NA))
bdata <- bdata[!is.na(bdata$RT),] 
```

### Add additional variables of interest
```{r}
CorrectRT <-  ifelse(bdata$Accuracy==1, bdata$RT, NA); 
IncorrectRT <- ifelse(bdata$Accuracy==0, bdata$RT, NA); 
CorrectConfidence <- ifelse(bdata$Accuracy==1, bdata$Confidence, NA); 
IncorrectConfidence <- ifelse(bdata$Accuracy==0, bdata$Confidence, NA); 

bdata <- cbind(bdata, CorrectRT, IncorrectRT, CorrectConfidence, IncorrectConfidence)
rm(CorrectRT,IncorrectRT,CorrectConfidence,IncorrectConfidence)
```

#### **Accuracy  - Recall**
```{r message=TRUE, paged.print=TRUE}

recall <- subset(bdata, Run == "1")
xtabs( ~ RespType + StimType, recall)


g_bdata <- ddply(recall, c("S_ID","StimType", "RespType"), summarise,
                  N = sum(!is.na(trial)),
                  meanRespType = N/192, 
                  meanRespTypePerc = meanRespType*100,
                  medianRT = median(RT, na.rm=TRUE),
                 meanRT = mean(RT, na.rm=TRUE),
                  mean_Conf = mean(Confidence, na.rm=TRUE)
)

g_bdata <- g_bdata[!is.na(g_bdata$RespType),]  # Getting rid of the few omissions in the dataset
g_bdata$RespType <- factor(g_bdata$RespType,levels = c("Correct", "Foil", "Distractor"))


### Means to report
 g_bdata  %>%
  group_by(StimType, RespType) %>%
  summarise_at(vars(meanRespTypePerc), list(mean = mean, std = sd))
 
 
# ---------- Multinomial logistic regression ---------------------
# Does the number of responses per response type vary for different stimulation conditions
recall$RespType <- relevel(recall$RespType, ref = "Correct")
m.acc <- nnet::multinom(RespType ~ StimType, data = recall)
summary(m.acc)
exp(coef(m.acc))


# Check the Z-score for the model (wald Z)
z <- summary(m.acc)$coefficients/summary(m.acc)$standard.errors
z
p <- (1 - pnorm(abs(z), 0, 1))*2
p

Anova(m.acc)

# ---- Group data for plotting -----

g_data <- ddply(recall, c("S_ID","StimType","session"), summarise,
                sum_acc = sum(Accuracy),
                sum_acc_perc = (sum_acc/192)*100,
                mean_acc = mean(Accuracy),
                sd_acc = sd(Accuracy),
                se_acc = se(Accuracy)
)

## Plot Accuracy 
p.RespType <- ggplot(g_bdata, aes(x = RespType, y = meanRespTypePerc, fill = StimType))  + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.9)) +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = position_dodge(0.9), size = 0.6, width = 0.3, colour="black") + geom_dotplot(binaxis='y', stackdir='center', position=position_dodge(0.9), stackratio=1, dotsize=0.15) +
  scale_y_continuous(name = "Mean Response (%)",
                           breaks = seq(0, 100, 20),
                           limits=c(0, 100)) +
      theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
   scale_x_discrete(breaks=c("Correct","Foil", "Distractor"),
        labels=c("Target","Foil", "Distractor")) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3"))

p.RespType
ggsave(p.RespType, filename = "Figure_5A.pdf",  width = 11, height = 9, dpi = 300, units = "cm", device = "pdf")  


# ---------------------------------------------------------------------------------
#---------------- Binomial --------------------------
m1 <- glmer(Accuracy ~ StimType + (1|S_ID) + (1|session), data=recall, family = binomial(link = "logit"), control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5)))

m2<- glmer(Accuracy ~ StimType + (1|S_ID) + (1|session) + (1|block), data=recall, family = binomial(link = "logit"), control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5)))

m3 <- glmer(Accuracy ~ StimType + (1|S_ID) + (1|session) + (1|block/trial), data=recall, family = binomial(link = "logit"), control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5)))

anova(m1, m2, m3)
lmtest:::lrtest(m1, m2, m3)
# keeping m2

Anova(m2)
summary(m2)

library(DHARMa)
testDispersion(m2)
simulationOutput <- simulateResiduals(fittedModel = m2, plot = T)
emm2 = emmeans(m2, specs = "StimType")
emm2
emmeans(m2, pairwise ~ StimType, type="response")
pairs(emm2, reverse = TRUE, type="response")

fit <- as.data.frame(emm2)  
g_data <- ddply(recall, c("S_ID","StimType"), summarise,
                mean_acc = mean(Accuracy))

## Plot Accuracy - binomial
p <- ggplot(data = fit, mapping=aes(x=StimType, y=emmean*100, ymin=(emmean-SE)*100, ymax=(emmean+SE)*100)) +
  geom_pointrange(size=0.9, alpha=0.8, color= c("#747674", "#D16103")) +
  scale_y_continuous(name = "Estimated Mean Accuracy (%)",
                     limits=c(20, 100)) +
  theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
        axis.text.x = element_text(color = "grey20", size = 14, angle = 45, face = "bold", hjust = 1),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
        legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  theme(strip.text.x = element_text(size = 14),
        strip.text.y = element_text(size = 20)) + 
  ggtitle("") + xlab("")  + scale_color_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3")) 

p
ggsave(p, filename = "Figure_5b.pdf",  width = 4, height = 9, dpi = 300, units = "cm", device = "pdf")  

```

#### **Reaction Times - Recall**
```{r message=TRUE, paged.print=TRUE}
# plotting the data
library(ggridges)
ggplot(recall, aes(x = RT, fill = RespType)) +
                    geom_histogram(bins = 30) +
                    facet_grid(StimType ~ RespType)


pander(recall %>% 
    group_by(RespType,StimType) %>% 
    summarise(median(RT), sd(RT)))

# Does reaction time per response type vary for different stimulation conditions?

# Using glm without random effects to find starting values for the optimisation

m0 <- glm(RT ~ StimType*RespType, data=recall, family = inverse.gaussian(link=identity))

m1 <- glmer(RT ~ StimType*RespType +  (1|S_ID) + (1|session),
            data = recall,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))

m2 <- glmer(RT ~ StimType*RespType +  (1|S_ID) + (1|block) + (1|session),
            data = recall,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


m3 <- glmer(RT ~ StimType*RespType +  (1|S_ID) + (1|session) + (1|block/trial),
            data = recall,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))

anova(m1, m2, m3)
lmtest:::lrtest(m1, m2, m3)


# keeping m3
plot(m3)
qqnorm(resid(m3))
qqline(resid(m3))

Anova(m3)
summary(m3)

estimated_means_RTall <- emmeans(m3, pairwise ~ StimType | RespType, type="response")



# -- Does reaction time for correct vs incorrect vary for different stimulation conditions
m0 <- glm(RT ~ StimType*Accuracy, data=recall, family = inverse.gaussian(link=identity))

m2 <- glmer(RT ~ StimType*Accuracy +  (1|S_ID) + (1|session) + (1|block),
            data = recall,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


m3 <- glmer(RT ~ StimType*Accuracy +  (1|S_ID) + (1|session) + (1|block/trial),
            data = recall,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


anova(m0, m2, m3)
lmtest:::lrtest(m0, m2, m3)

plot(m3)
qqnorm(resid(m3))
qqline(resid(m3))

Anova(m3)
plot_model(m3)


pander(recall %>% 
    group_by(Accuracy,StimType) %>% 
    summarise(median(RT), sd(RT)))

# Check RT for correct Trials only -
# 
recall_correct <- subset(recall, Accuracy=="1")

m0 <- glm(RT ~ StimType, data=recall_correct, family = inverse.gaussian(link=identity))

m2 <- glmer(RT ~ StimType +  (1|S_ID) + (1|block) + (1|session),
            data = recall_correct,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))

m3 <- glmer(RT ~ StimType +  (1|S_ID) + (1|session) + (1|block/trial),
            data = recall_correct,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


anova(m0, m2, m3)
lmtest:::lrtest(m0, m2, m3)
Anova(m2)


## Plot RT

p.RespTypeRT <- ggplot(g_bdata, aes(x = RespType, y = medianRT, fill = StimType))  + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.9)) +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = position_dodge(0.9), size = 0.6, width = 0.3, colour="black") + geom_dotplot(binaxis='y', stackdir='center', position=position_dodge(0.9), stackratio=1, dotsize=0.15) +
  scale_y_continuous(name = "Median RT (s)",
                           breaks = seq(0, 8, 2),
                           limits=c(0, 8)) +
      theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
   scale_x_discrete(breaks=c("Correct","Foil", "Distractor"),
        labels=c("Target","Foil", "Distractor")) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3"))

p.RespTypeRT
ggsave(p.RespTypeRT, filename = "Figure_5D.pdf",  width = 11, height = 9, dpi = 300, units = "cm", device = "pdf") 
```

#### **Confidence -- Recall**
```{r message=TRUE, paged.print=TRUE}
    
xtabs( ~ rConf + RespType + StimType, recall)
# Removing confidence = 0 > no response 
recall$rConf <- as.numeric(recall$rConf)
sum(recall$rConf=="0")

Confidence_omission_Prct <- (sum(data_raw$rConf=="0")/length(data_raw$rConf))*100
Confidence_omission_Prct

recall <- recall%>% mutate(rConf = replace(rConf, rConf=="0", NA))
recall <- recall[!is.na(recall$rConf),] 

# Observed means
pander(recall %>% 
    group_by(RespType,StimType) %>% 
    summarise(mean(rConf), sd(rConf)))

# Stats
recall$rConf <- as.factor(recall$rConf)


ggplot(data = recall) + 
  geom_bar(mapping = aes(x = rConf, fill = RespType)) + facet_wrap(.~StimType)

# Does the accuracy per response type vary for different stimulation conditions
library(ordinal)
library(ggeffects)

recall$rConf  <- factor(recall$rConf, 
                           ordered=TRUE)


m1 = clmm(rConf ~ RespType*StimType + (1|S_ID), data = recall, Hess = TRUE)
m2 = clmm(rConf ~ RespType*StimType + (1|S_ID) + (1|block), data = recall, Hess = TRUE)
#m3 = clmm(rConf ~ RespType*StimType + (1|S_ID) + (1|session), data = recall, Hess = TRUE)
# cannot model session in random effects because only 2 levels are available

anova(m1,m2)

library(RVAideMemoire)
Anova.clmm (m2)
summary(m2)

emmeans.conf <- emmeans(m2, ~ RespType | StimType, mode = "mean.class")
emmeans.conf
# Comparing confidence across correct and incorrect responses
# 

m3 = clmm(rConf ~ as.factor(Accuracy)*StimType + (1|S_ID) + (1|block), data = recall, Hess = TRUE)
Anova.clmm(m3)
summary(m3)
emmeans(m3, ~ StimType | Accuracy, mode = "mean.class")


# Comparing confidence for correct responses only
recall_correct <- subset(recall, Accuracy=="1")
xtabs( ~ rConf +  StimType, recall_correct)

m4 = clmm(rConf ~ StimType + (1|S_ID) + (1|block), data = recall, Hess = TRUE)
Anova.clmm(m4)
summary(m4)
emmeans(m4, ~  StimType)

## Plot Confidence
g_data <- ddply(recall, c("S_ID","StimType","RespType"), summarise,
                sum_acc = sum(Accuracy),
                sum_acc_perc = (sum_acc/192)*100,
                mean_acc = mean(Accuracy),
                mean_acc_perc = mean_acc*100,
                sd_acc = sd(Accuracy),
                se_acc = se(Accuracy),
                mean_conf = mean(Confidence)
)

g_data$RespType <- factor(g_data$RespType, levels = c("Correct",  "Foil", "Distractor"), ordered = TRUE)


p.Conf <- ggplot(g_data, aes(x = RespType, y = mean_conf , fill = StimType))  + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.9)) +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = position_dodge(0.9), size = 0.6, width = 0.3, colour="black") + geom_dotplot(binaxis='y', stackdir='center', position=position_dodge(0.9), stackratio=1, dotsize=0.15) +
  scale_y_continuous(name = "Mean Confidence",
                           breaks = seq(0, 4, 1),
                           limits=c(0, 4)) +
      theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
    scale_x_discrete(breaks=c("Correct","Foil", "Distractor"),
        labels=c("Target","Foil", "Distractor")) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3"))

p.Conf
ggsave(p.Conf, filename = "Figure_5F.pdf",  width = 11, height = 9, dpi = 300, units = "cm", device = "pdf")  

```

#### **Accuracy  - Re-test**
```{r message=TRUE, paged.print=TRUE}

retest <- subset(bdata, Run == "2")
xtabs( ~ RespType + StimType, retest)

# ---------- Multinomial logistic regression ---------------------
# Does the number of responses per response type vary for different stimulation conditions
retest$RespType <- relevel(retest$RespType, ref = "Correct")
m.acc <- nnet::multinom(RespType ~ StimType, data = retest)
summary(m.acc)
exp(coef(m.acc))

# Check the Z-score for the model (wald Z)
z <- summary(m.acc)$coefficients/summary(m.acc)$standard.errors
z
p <- (1 - pnorm(abs(z), 0, 1))*2
p

Anova(m.acc)


#---------------- Binomial --------------------------
m1 <- glmer(Accuracy ~ StimType + (1|S_ID) + (1|session), data=retest, family = binomial(link = "logit"), control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5)))

m2<- glmer(Accuracy ~ StimType + (1|S_ID) + (1|session) + (1|block), data=retest, family = binomial(link = "logit"), control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5)))

m3 <- glmer(Accuracy ~ StimType + (1|S_ID) + (1|session) + (1|block/trial), data=retest, family = binomial(link = "logit"), control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5)))

anova(m1, m2, m3)
lmtest:::lrtest(m1, m2, m3)
# keeping m2

Anova(m2)
summary(m2)

library(DHARMa)
testDispersion(m2)
simulationOutput <- simulateResiduals(fittedModel = m2, plot = T)

## Plot - Fig S8
g_bdata <- ddply(retest, c("S_ID","StimType", "RespType"), summarise,
                  N = sum(!is.na(trial)),
                  meanRespType = N/192, 
                  meanRespTypePerc = meanRespType*100,
                  medianRT = median(RT, na.rm=TRUE),
                 meanRT = mean(RT, na.rm=TRUE),
                  mean_Conf = mean(Confidence, na.rm=TRUE)
)


p.RespType <- ggplot(g_bdata, aes(x = RespType, y = meanRespTypePerc, fill = StimType))  + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.9)) +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = position_dodge(0.9), size = 0.6, width = 0.3, colour="black") + geom_dotplot(binaxis='y', stackdir='center', position=position_dodge(0.9), stackratio=1, dotsize=0.15) +
  scale_y_continuous(name = "Mean Response (%)",
                           breaks = seq(0, 100, 20),
                           limits=c(0, 100)) +
      theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
   scale_x_discrete(breaks=c("Correct","Foil", "Distractor"),
        labels=c("Target","Foil", "Distractor")) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3"))

p.RespType
ggsave(p.RespType, filename = "Figure_S8A.tiff",  width = 11, height = 9, dpi = 300, units = "cm", device = "tiff")  

```

#### **Reaction Times - Re-test**
```{r message=TRUE, paged.print=TRUE}
# plotting the data
library(ggridges)
ggplot(retest, aes(x = RT, fill = RespType)) +
                    geom_histogram(bins = 30) +
                    facet_grid(StimType ~ RespType)

pander(retest %>% 
    group_by(RespType,StimType) %>% 
    summarise(median(RT), sd(RT)))

# Does reaction time per response type vary for different stimulation conditions?

# Using glm without random effects to find starting values for the optimisation

m0 <- glm(RT ~ StimType*RespType, data=retest, family = inverse.gaussian(link=identity))

m1 <- glmer(RT ~ StimType*RespType +  (1|S_ID) + (1|session),
            data = retest,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))

m2 <- glmer(RT ~ StimType*RespType +  (1|S_ID) + (1|block) + (1|session),
            data = retest,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


m3 <- glmer(RT ~ StimType*RespType +  (1|S_ID) + (1|session) + (1|block/trial),
            data = retest,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


anova(m1, m2, m3)
lmtest:::lrtest(m1, m2, m3)


# keeping m3
plot(m3)
qqnorm(resid(m3))
qqline(resid(m3))

Anova(m3)

# -- Does reaction time for correct vs incorrect vary for different stimulation conditions
m0 <- glm(RT ~ StimType*Accuracy, data=retest, family = inverse.gaussian(link=identity))

m2 <- glmer(RT ~ StimType*Accuracy +  (1|S_ID) + (1|session) + (1|block),
            data = retest,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


m3 <- glmer(RT ~ StimType*Accuracy +  (1|S_ID) + (1|session) + (1|block/trial),
            data = retest,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


anova(m0, m2, m3)
lmtest:::lrtest(m0, m2, m3)

plot(m3)
qqnorm(resid(m3))
qqline(resid(m3))

Anova(m3)
summary(m3)
plot_model(m3)

estimated_means <- emmeans(m3, specs = "StimType")
estimated_means 


# Check RT for correct Trials only -
# 
retest_correct <- subset(retest, Accuracy=="1")

m0 <- glm(RT ~ StimType, data=retest_correct, family = inverse.gaussian(link=identity))

m2 <- glmer(RT ~ StimType +  (1|S_ID) + (1|block) + (1|session),
            data = retest_correct,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))

m3 <- glmer(RT ~ StimType +  (1|S_ID) + (1|session) + (1|block/trial),
            data = retest_correct,
            family = inverse.gaussian(link=identity),
            start=list(fixef=coef(m0)),
            control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun=2e5), nAGQ0initStep=FALSE))


anova(m0, m2, m3)
lmtest:::lrtest(m0, m2, m3)
Anova(m2)
summary(m2)

## Plot RT re-test
## 
g_bdata <- ddply(retest, c("S_ID","StimType", "RespType"), summarise,
                  N = sum(!is.na(trial)),
                  meanRespType = N/192, 
                  meanRespTypePerc = meanRespType*100,
                  medianRT = median(RT, na.rm=TRUE),
                  meanRT = mean(RT, na.rm=TRUE),
                  mean_Conf = mean(Confidence, na.rm=TRUE)
)

p.RespTypeRT <- ggplot(g_bdata, aes(x = RespType, y = medianRT, fill = StimType))  + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.9)) +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = position_dodge(0.9), size = 0.6, width = 0.3, colour="black") + geom_dotplot(binaxis='y', stackdir='center', position=position_dodge(0.9), stackratio=1, dotsize=0.15) +
  scale_y_continuous(name = "Median RT (s)",
                           breaks = seq(0, 8, 2),
                           limits=c(0, 8)) +
      theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
   scale_x_discrete(breaks=c("Correct","Foil", "Distractor"),
        labels=c("Target","Foil", "Distractor")) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3"))

p.RespTypeRT
ggsave(p.RespTypeRT, filename = "Figure_S8B.tiff",  width = 11, height = 9, dpi = 300, units = "cm", device = "tiff")  

```

#### **Recall and Re-test** 
```{r message=TRUE, paged.print=TRUE}

g_bdata <- ddply(bdata, c("S_ID","StimType", "RespType","Run"), summarise,
                  N = sum(!is.na(trial)),
                  meanRespType = N/192, 
                  meanRespTypePerc = meanRespType*100,
)

### Means to report
 g_bdata  %>%
  group_by(StimType, RespType, Run) %>%
  summarise_at(vars(meanRespType), list(mean = mean, std = sd))

bdata$RespType <- relevel(bdata$RespType, ref = "Correct")
m.acc <- nnet::multinom(RespType ~ StimType*Run, data = bdata)
summary(m.acc)
exp(coef(m.acc))


# Check the Z-score for the model (wald Z)
z <- summary(m.acc)$coefficients/summary(m.acc)$standard.errors
z
p <- (1 - pnorm(abs(z), 0, 1))*2
p

Anova(m.acc)

```

#### **Recall - Re-test detailed** 
```{r message=TRUE, paged.print=TRUE}

# Check answers face-name pair recall to re-test
NameC1 <-  ifelse(recall$Accuracy==1, recall$Name, NA)   
recall$NameC1 <- NameC1 

id = unique(bdata$S_ID)
cond <- vector()
for (i in 1:length(unique(retest$S_ID))) {
  for (s in 1:length(unique(retest$session))) {
    tmp_df = subset(recall, S_ID==id[i] & session==s)
    tmp_df2 = subset(retest, S_ID==id[i] & session==s)
    print(paste("Subject", id[i], "session", s))
    ntrial_tmp = length(unique(tmp_df2$Name))
    for (n in 1:ntrial_tmp) {
      m <- match(tmp_df2$Name[n],tmp_df$NameC1)
      if (!is.na(m)){
        cond <- c(cond, 1)
      } else {
        cond <- c(cond, 0)
      }
    }
    }
}

retest$Correct_Rec <- cond


### Re-test memory fates

retest$type_memory = ifelse(retest$Accuracy==1 & retest$Correct_Rec==1,"Remembered",
                             ifelse(retest$Accuracy==0 & retest$Correct_Rec==1, "Forgotten",
                                    ifelse(retest$Accuracy==1 & retest$Correct_Rec==0, "Retrived",
                                           ifelse(retest$Accuracy==0 & retest$Correct_Rec==0, "Never",NA))))


retest$type_transition = ifelse(retest$Accuracy==1 & retest$Correct_Rec==1,"T2T",
                             ifelse(retest$RespType=="Foil" & retest$Correct_Rec==1, "T2F",
                                    ifelse(retest$RespType=="Distractor" & retest$Correct_Rec==1, "T2D",
                                      ifelse(retest$Accuracy==1 & retest$Correct_Rec==0, "CR",
                                           ifelse(retest$Accuracy==0 & retest$Correct_Rec==0, "Never",NA)))))

retest$remembered = ifelse(retest$Accuracy==1 & retest$Correct_Rec==1,1,
                             ifelse(retest$Accuracy==0 & retest$Correct_Rec==1, 0,
                                    ifelse(retest$Accuracy==1 & retest$Correct_Rec==0, 0,
                                           ifelse(retest$Accuracy==0 & retest$Correct_Rec==0, 0,NA))))


## What happens at re-test to the face-name associations previously learned (i.e. target at recall)?

knew <- subset(retest, Correct_Rec=="1")
knew.g <- ddply(knew, c("S_ID","StimType"), summarise,
                t1 = sum(Correct_Rec),
                t2 = sum(remembered)
)

library(data.table)
long <- melt(setDT(knew.g), id.vars = c("S_ID","StimType"), variable.name = "time")

m2<- lmer(value ~ StimType*time + (1|S_ID), data=long)
Anova(m2)


## Plot Recall and Re-test mean accuracy for pairs correctly encoded first time around
df2 <- long %>%
  group_by(StimType, time) %>%
  summarise(acc.mean = (mean(value)/192)*100,
            acc.se = (se(value)/192)*100)

p.Acc.t <- ggplot(subset(df2, StimType=="TI 1:3"), aes(x=time, y=acc.mean, group=StimType, color=StimType, palette = c("#747674", "#D16103"))) + 
  geom_line(color = "#D16103") +
  geom_pointrange(aes(ymax=acc.mean+acc.se, ymin=acc.mean), color="#D16103") +
  geom_line(data = subset(df2, StimType=="Sham"), color = "#747674") +
  geom_pointrange(data = subset(df2, StimType=="Sham"), aes(ymax=acc.mean, ymin=acc.mean-acc.se), color = "#747674") +
  scale_y_continuous(name = "Mean Accuracy (%)") +
  theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 45, face = "bold", hjust = 1),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  scale_x_discrete(name ="", 
                   labels=c("t1" = "Recall", "t2" = "Re-test")) +
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3"))

p.Acc.t
ggsave(p.Acc.t, filename = "Figure_5C.pdf",  width = 5, height = 9.2, dpi = 300, units = "cm", device = "pdf") 



## Fate of all answers from recall to re-test
retest$type_transition <- as.factor(retest$type_transition)
retest$type_transition <- relevel(retest$type_transition, ref = "T2T")
m.acc <- nnet::multinom(type_transition ~ StimType, data = retest)
summary(m.acc)
exp(coef(m.acc))


# Check the Z-score for the model (wald Z)
z <- summary(m.acc)$coefficients/summary(m.acc)$standard.errors
z
p <- (1 - pnorm(abs(z), 0, 1))*2
p

Anova(m.acc)
summary(m.acc)

emmeans(m.acc, pairwise ~ StimType | type_transition, adjust="tukey", mode = "prob")

g_bdata <- ddply(retest, c("S_ID","StimType", "type_transition"), summarise,
                  N = sum(!is.na(trial)),
                  meanRespType = N/192,
                  meanRespTypePerc = meanRespType*100,
                  medianRT = median(RT, na.rm=TRUE),
                 meanRT = mean(RT, na.rm=TRUE)
)


level_order <- c('T2T', 'T2F', 'T2D','CR', 'Never') 
label_name <- c('Target->Target', 'Target->Foil', 'Target->Distractor','Incorrect->Target', 'Incorrect->Incorrect') 

p.Transi <- ggplot(g_bdata, aes(x = type_transition, y = meanRespTypePerc , fill = StimType))  + 
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.9)) +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = position_dodge(0.9), size = 0.6, width = 0.3, colour="black") + geom_dotplot(binaxis='y', stackdir='center', position=position_dodge(0.9), stackratio=1, dotsize=0.15) +
  scale_y_continuous(name = "Mean Response (%)",
                           breaks = seq(0, 100, 20),
                           limits=c(0, 100)) +
      theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 45, face = "bold", hjust = 1),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
   scale_x_discrete(limits = level_order, 
                    breaks=level_order,
                    labels=label_name) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3")) 

p.Transi
ggsave(p.Transi, filename = "Figure_S8C.tiff",  width = 11, height = 12, dpi = 300, units = "cm", device = "tiff")  

```

#### **Recall - Re-test RT** 
```{r message=TRUE, paged.print=TRUE}
## 
## RT for correct trials
recall_correct <-  subset(recall, Accuracy=="1")
df.ir <- recall_correct %>%
  group_by(StimType, S_ID) %>%
  summarise(t1 = median(CorrectRT))

retest_correct <-  subset(retest, Accuracy=="1")
df.lr <- retest_correct %>%
  group_by(StimType, S_ID) %>%
  summarise(t2 = median(CorrectRT))

RTall <- merge(df.ir,df.lr,by=c("S_ID","StimType")) 
long <- melt(setDT(RTall), id.vars = c("S_ID","StimType"), variable.name = "time")

m2<- lmer(value ~ StimType*time + (1|S_ID), data=long)
Anova(m2)

df2 <- long %>%
  group_by(StimType, time) %>%
  summarise(mean = mean(value),
            se = se(value))

p.RT.t <- ggplot(subset(df2, StimType=="TI 1:3"), aes(x=time, y=mean, group=StimType, color=StimType, palette = c("#747674", "#D16103"))) + 
  geom_line( color = "#D16103") +
  geom_pointrange(aes(ymax=mean+se, ymin=mean), color="#D16103") +
  geom_line(data = subset(df2, StimType=="Sham"), color = "#747674") +
  geom_pointrange(data = subset(df2, StimType=="Sham"), aes(ymax=mean, ymin=mean-se), color = "#747674") +
  scale_y_continuous(name = "Median Target RT (s)",
                     breaks=c(seq(3,4,0.5)), limits = c(3, 4)) +
  theme(plot.title = element_text(color="black", size=14, face="bold", hjust = 0.5),
          axis.text.x = element_text(color = "grey20", size = 14, angle = 45, face = "bold", hjust = 1),
        axis.text.y = element_text(color = "grey20", size = 14, angle = 0, face = "plain"),  
        axis.title.x = element_text(color = "grey20", size = 14, angle = 0, face = "bold"),
        axis.title.y = element_text(color = "grey20", size = 14, angle = 90, face = "bold"),
            legend.text = element_blank(),
        legend.background = element_blank(),
        legend.key=element_blank(),
        panel.background = element_blank(),
        legend.title=element_blank()) +
         theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  scale_x_discrete(name ="", 
                   labels=c("t1" = "Recall", "t2" = "Re-test")) +
    theme(strip.text.x = element_text(size = 14),
          strip.text.y = element_text(size = 20),
          legend.text = element_text(size=14),
          legend.key.size = unit(0.5, 'cm')) + ggtitle("") + xlab("")  + scale_fill_manual(values = c("#747674", "#D16103"), name = "", labels = c("Sham", "TI 1:3")) 

p.RT.t
ggsave(p.RT.t, filename = "Figure_5E.pdf",  width = 5, height = 9.2, dpi = 300, units = "cm", device = "pdf")  

```

**Stimulation Duration**
```{r message=FALSE, warning=FALSE}
# Import data
data_raw <- read_csv("FNAT_stimduration.csv")

# Assign appropriate Stim factors
data_raw$StimType <- factor(data_raw$StimType)
levels(data_raw$StimType) <- c("Sham", "TI 1:3")

# Assign factors
data_raw$StimType <- factor(data_raw$StimType)
data_raw$S_ID <- factor(data_raw$S_ID)
data_raw$Run <- factor(data_raw$Run)


## Check how long it took participants to respond for Run 1 and Run 2 

data_raw %>% group_by(StimType, Run) %>% 
  summarise(mean = mean(stimdur_min),
            sd = sd(stimdur_min), min = min(stimdur_min), max = max(stimdur_min))


# Select only stimulation and Run 1 -- only run 1 got stimulation
TIdur <- subset(data_raw, StimType=="TI 1:3" & Run=="1")

# Descriptives for duration - average over subject 

g_dur <- ddply(TIdur, c("S_ID"), summarise,
                     
         stimdur_min = sum(stimdur_min, na.rm=TRUE))

g_dur %>% summarize(mean = mean(stimdur_min),
            sd = sd(stimdur_min), min = min(stimdur_min), max = max(stimdur_min))


# Correlate the duration of stimulation with accuracy in the recall during stimulation

g_recall_TI <- ddply(subset(recall, StimType=="TI 1:3"), c("S_ID"), summarise,
                mean_acc_recall = mean(Accuracy),
                mean_acc_perc_recall = mean_acc_recall*100
)

total <- merge(g_recall_TI, g_dur, by=c("S_ID"))


library("ggpubr")
ggscatter(total, x = "stimdur_min", y = "mean_acc_recall", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Stimulation Duration", ylab = "Accuracy Recall") 


# Correlate the duration of stimulation with accuracy in the re-test 
g_retest_TI <- ddply(subset(retest, StimType=="TI 1:3"), c("S_ID"), summarise,
                mean_acc_retest = mean(Accuracy),
                mean_acc_perc_retest = mean_acc_retest*100
)
total <- merge(g_retest_TI, g_dur, by=c("S_ID"))


ggscatter(total, x = "stimdur_min", y = "mean_acc_retest", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Stimulation Duration", ylab = "Accuracy Retest") 


g_dur %>% summarize(mean = mean(stimdur_min+10),
            sd = sd(stimdur_min+10), min = min(stimdur_min+10), max = max(stimdur_min+10))



# Sum task durations

g.durations <- ddply(data_raw, c("S_ID","StimType", "Run"), summarise,
                sum = sum(stimdur_min),
                std = sd(stimdur_min)
)

g.durations %>% group_by(Run) %>% 
  summarise(mean = mean(sum),
            sd = sd(sum), min = min(sum), max = max(sum))

```

