---
title: "Motion Parameters"
output:
  pdf_document: default
  html_document:
    
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---
### Data
The notebook includes data from:

  1. Motion parameters (DVARS) derived from running fsl_motion_outliers for all subjects 
  2. Additional motion parameters derived from extracting DVARS and sDVARS (from https://github.com/nicholst/StandardizedDVARS/blob/master/DVARS.sh)

### Libraries
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Clear environment
rm(list = ls())

# Get Libraries and Functions
source("~/Dropbox (Personal)/TI_paper/ti-paper/Data/Functions.R")

```

### Import data 
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
setwd("~/Dropbox (Personal)/TI_paper/ti-paper/Data/MRI/FaceNameTask/Motion")
motion <- read.csv("MotionData.csv")

```

### Check for Outliers 
```{r}
# Calculate outlier percentage
Percent_outlier <- (motion$outliers / motion$nvols)*100
motion <- cbind(motion, Percent_outlier)

Outlier <-  ifelse(motion$Percent_outlier >20,1,0)  
motion <- cbind(motion, Outlier)
rm(Outlier)

# Subjects to exclude from analysis
ID_outliers <- subset(motion, Outlier==1)
unique(ID_outliers$S_ID)
```

### Import data with motion metrics per stimulation condition - This was done using the script ExtractMotionPerCondition.m

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
MotionCond <- read_csv("MotionPerCond.csv")

# Assign factors
# TI 1:1, TI 1:3 and Sham are during encoding; resp = response period across conditions

MotionCond$metric <- factor(MotionCond$metric)
MotionCond$StimType <- factor(MotionCond$StimType)

# Based on previous identification of outliers excluding TIDES_P2T_S4	
MotionCond <- subset(MotionCond, S_ID!="TIDES_P2T_S4")
```

### Calculate mean values for reporting

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
MotionCond %>% 
  group_by(StimType,metric) %>% 
  summarise(average = mean(meanMotion), std = sd(meanMotion))

```

### Calculate DVARS per Stim Condition

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Compare DVARS across stim conditions
# Excluding resp period for now - could be compared later to each condition or the average of stim conditions (?), also excluding mean_all
FN.Motion.DVARS <- subset(MotionCond, metric=="DVARS" & StimType!="resp" & StimType!="mean_all")

DVARSfit <- lmer(meanMotion ~ StimType + (1|S_ID), data = FN.Motion.DVARS)
Anova(DVARSfit, test="F")
summary(DVARSfit, ddf ="Kenward-Roger")


estimated_means <- get_means(DVARSfit, "StimType")
pander(estimated_means)

boxplot_DVARS <- ggplot(FN.Motion.DVARS, aes(x=StimType, y=meanMotion, fill=StimType)) + 
  geom_boxplot() + 
  geom_dotplot(binaxis='y', stackdir='center', dotsize = 0.5)
boxplot_DVARS + scale_fill_brewer(palette="Blues") + ggtitle("DVARS (fsl_motion_outliers) per condition") +
  xlab("Stimulation Type") + ylab("DVARS (fsl)")

```

### Calculate sDVARS per Stim Condition

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Compare sDVARS across stim conditions
# Excluding resp period for now - could be compared later to each condition or the average of stim conditions (?), also excluding mean_all
FN.Motion.sDVARS <- subset(MotionCond, metric=="sDVARS" & StimType!="resp" & StimType!="mean_all")

sDVARSfit <- lmer(meanMotion ~ StimType + (1|S_ID), data = FN.Motion.sDVARS)
anova.m1 = anova(DVARSfit)
print(anova.m1)

pander(anova.m1)

estimated_means <- get_means(sDVARSfit, "StimType")
pander(estimated_means)

boxplot_sDVARS <- ggplot(FN.Motion.sDVARS, aes(x=StimType, y=meanMotion, fill=StimType)) + 
  geom_boxplot() + 
  geom_dotplot(binaxis='y', stackdir='center', dotsize = 0.5)
boxplot_sDVARS + scale_fill_brewer(palette="Blues") + ggtitle("standardise DVARS per condition") +
  xlab("Stimulation Type") + ylab("sDVARS")
```
